Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-18 final_metrics_analysis.Rmd
moving median defendant EDA chunk

```{r py setup, include=FALSE}
library(reticulate)
use_condaenv("anaconda3")
```

@@

# Exploratory Data Analysis
```{python exploratory visualization set up}
df_viz = X_new.copy()
df_viz['race'] = X_new['race'].replace({1.0: 'Caucasian', 0.0: 'African-American'})
df_viz['two_year_recid'] = y_new.replace({1:'Recidivated', 0: 'Survived'})
df_viz.index = df_viz.index.droplevel('race')

@@

```{python} 
ep = EqOddsPostprocessing(unprivileged_groups=0, privileged_groups= 1, seed =1234567)
eo = PostProcessingMeta(estimator=lr, postprocessor=ep, random_state=1234567)
eo.fit(train_BLD, test_BLD)
y_pred_EO = eo.predict(test_BLD)
#y_proba_EO = eo.predict_(test_BLD)

>>>>

```{r py setup, include=FALSE}
library(reticulate)
#use_condaenv("anaconda3")
```

@@

# Exploratory Data Analysis

```{python exploratory visualization set up}
df_viz = X_new.copy()
df_viz['race'] = X_new['race'].replace({1.0: 'Caucasian', 0.0: 'African-American'})
df_viz['two_year_recid'] = y_new.replace({1:'Recidivated', 0: 'Survived'})
df_viz.index = df_viz.index.droplevel('race')

@@

```{python} 
#ep = EqOddsPostprocessing(unprivileged_groups=0, privileged_groups= 1, seed =1234567)
#eo = PostProcessingMeta(estimator=lr, postprocessor=ep, random_state=1234567)
#eo.fit(train_BLD, test_BLD)
#y_pred_EO = eo.predict(test_BLD)
#y_proba_EO = eo.predict_(test_BLD)
